Untwisting the Boerdijk-Coxeter Helix

### 2017-05-13 doc/TetrahelixUntwist.tex
removing glussbot name

The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closuporthog}, is
a face-to-face stack of tetrahedra that winds about a straight axis.
Because architects, structural engineers, and roboticists are inspired
by and follow such regular mathematical models but can also build structures and
machines of differing or even dynamically changing length, it is
useful to develop the mathematics of structures formed from tetrahedra
where we relax regularity.

The vertices of the tetrahedra lie upon
three helices about the central axis.
The \\
Glussbot\cite{readglussbot} (or Tetrobot)\cite{TetrobotBook} uses the regularity of
this geometry to make a tentacle-like robot that can crawl like a slug
or mollusc.  These modular robotic systems use mechanical actuators which can change their length, connected by special joints,
such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint in the case of the Glussbot, or the CMS joint\cite{HamlinSandersonCMS}, in the case of the Tetrobot,
which allow many members to meet in a single point.
Such machines can
follow purely regular mathematical models such as the Boerdijk–-Coxeter
helix or the Octet Truss\cite{richard1961synergetic}.

@@

Imagining \cref{fig:closeup,fig:closeuporthog} as a static mechanical structure,
we observe that it is useful to the mechanical engineer or
roboticist because the structure remains an inherently rigid,
omni-triangulated space frame, which is
mechanically strong.
Then we can imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are a joint that supported sufficient angular displacement
for this to be possible. An example of such a machine is a glussbot, shown in \cref{fig:glussbot}.

@@

\Cref{fig:helixcomparison} illustrates this difference with a 7-tetrahedra BC helix, which is
in fact the same geometry as the robot illustrated in \cref{fig:glussbot}.
Although the nodes coincide,
\cref{graycoxeter} evaluated
at real values generates the black helix which runs through every node, and \cref{eq:colored} defines
the red, yellow, and blue helices. (In this figure
these rail helices have been rendered at a slightly higher radius than the nodes for clarity;
in actuality the maximum distance between the continuous, curved helix and the
straight edges between nodes is much smaller than can be clearly rendered.)

@@

\begin{figure}[H] %float with two figures
  \centering
     \includegraphics[width=0.9\textwidth]{figures/MedCantedCropped.png}
     \caption{Glussbot in relaxed, or BC helix configuration}
     \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
     \caption{The Equitetrabeam: Fully Untwisted Glussbot in Hexapod Configuration}
     \label{fig:glussbot}
\end{figure}

@@

\begin{theorem}
  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a glussbot
  forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane.
\end{theorem}

\begin{proof}
  Proof by our computer program that does this using Equation \eqref{eq:general} applied to the
  7-tet Tetrobot/Glussbot.

@@

The Gluss Project \url{http://pubinv.github.io/gluss/} is part of Public Invention \url{https://pubinv.github.io/PubInv/},
a free-libre, open-source research, hardware, and software project that welcomes volunteers.
It is our goal to organize projects for the benefit of all humanity without seeking profit or intellectual property.
To assist, contact \email{read.robert@gmail.com}.

>>>>

The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closeuporthog}, is
a face-to-face stack of tetrahedra that winds about a straight axis.
Because architects, structural engineers, and roboticists are inspired
by and follow such regular mathematical models but can also build structures and
machines of differing or even dynamically changing length, it is
useful to develop the mathematics of structures formed from tetrahedra
where we relax regularity.

The vertices of the tetrahedra lie upon
three helices about the central axis.
The Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
this geometry to make a tentacle-like robot that can crawl like a slug
or mollusc.  These modular robotic systems use mechanical actuators which can change their length, connected by special joints,
such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint or the CMS joint\cite{HamlinSandersonCMS} used in the original Tetrobot,
which allow many members to meet in a single point.
Such machines can
follow purely regular mathematical models such as the Boerdijk–-Coxeter
helix or the Octet Truss\cite{richard1961synergetic}.

@@

Imagining \cref{fig:closeup,fig:closeuporthog} as a static mechanical structure,
we observe that it is useful to the mechanical engineer or
roboticist because the structure remains an inherently rigid,
omni-triangulated space frame, which is
mechanically strong.
Then we can imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are a joint that supported sufficient angular displacement
for this to be possible. An example of such a machine is a Tetrobot,
shown in \cref{fig:tetrobot}.

@@

\Cref{fig:helixcomparison} illustrates this difference with a 7-tetrahedra BC helix, which is
in fact the same geometry as the robot illustrated in \cref{fig:tetrobot}.
Although the nodes coincide,
\cref{graycoxeter} evaluated
at real values generates the black helix which runs through every node, and \cref{eq:colored} defines
the red, yellow, and blue helices. (In this figure
these rail helices have been rendered at a slightly higher radius than the nodes for clarity;
in actuality the maximum distance between the continuous, curved helix and the
straight edges between nodes is much smaller than can be clearly rendered.)

@@

\begin{figure}[H] %float with two figures
  \centering
     \includegraphics[width=0.9\textwidth]{figures/MedCantedCropped.png}
     \caption{7-Tet Tetrobot in relaxed, or BC helix configuration}
     \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
     \caption{The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration}
     \label{fig:tetrobot}
\end{figure}

@@

\begin{theorem}
  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a tetrobot
  forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane.
\end{theorem}

\begin{proof}
  Proof by our computer program that does this using Equation \eqref{eq:general} applied to the
  7-tet Tetrobot.

@@

The Tetrobot Project \url{http://pubinv.github.io/gluss/} is part of Public Invention \url{https://pubinv.github.io/PubInv/},
a free-libre, open-source research, hardware, and software project that welcomes volunteers.
It is our goal to organize projects for the benefit of all humanity without seeking profit or intellectual property.
To assist, contact \email{read.robert@gmail.com}.
